### 2024-02-16 Data/AnalysisData/codebook_plot_23_data_reported_alpha.Rmd
starting to restructure the article based on feedback. Start on adding meta-analysis component to H2

---
title: "Codebook created on 2024-01-02 at 2024-01-02 11:37:22.192211"
output: github_document
---

@@

## Dataset description
The data contains 1925 cases and 4 variables.

@@

```{r}
summaries <- read.csv("codebook_plot_46_data_rev.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2024-02-14 at 2024-02-14 09:47:30.71879"
output: github_document
---

@@

## Dataset description
The data contains 9 cases and 4 variables.

@@

```{r}
summaries <- read.csv("codebook_plot_23_data_reported_alpha.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2024-02-16 Data/DataPackageProtocol.Rmd
starting to restructure the article based on feedback. Start on adding meta-analysis component to H2

>>>>

### plot_23_data_reported_alpha.csv

*Explanation:* Contains reported alpha reliability coefficients extracted from original articles from which such data was available, and for which data was available from the replications from the Many Labs data to calculate reliabilities for. The goal of this data was to be superimposed on top of figure 2 (plot_23_alpha) to compare calculated reliability coefficients with reported reliability coefficients.

-   **title:** The title of the article relating to the particular measure of that row, extracted from coded_data_original_shortened.csv

-   **graph_title:** author, year, and optional word indicating the specific measure. Relates directly to the indication of the measures as shown in figure 2 (plot_23_alpha).

-   **article_order:** numerical variable giving the index for placing the reliability coefficients in the right row in figure 2 (plot_23_alpha).

-   **coefficient:** the value for the reported alpha coefficient for the specific measure as extracted from the original article the measure was reported in.

### 2024-02-16 Data/IntermediateData/codebook_data_5.1.1_clean.Rmd
added the final data preparation step, and the models for H1 and H3.
failed attempt to include R results as numbers in text.
Opened up the Many Labs retrieved data for the project.
starting to restructure the article based on feedback. Start on adding meta-analysis component to H2

---
title: "Codebook created on 2023-11-06 at 2023-11-06 15:00:31.816934"
output: github_document
---

@@

## Dataset description
The data contains 471 cases and 22 variables.

>>>>

---
title: "Codebook created on 2024-02-16 at 2024-02-16 14:19:38.624634"
output: github_document
---

@@

## Dataset description
The data contains 471 cases and 16 variables.

### 2024-02-16 Data/IntermediateData/codebook_data_5.1.2_clean.Rmd
starting to restructure the article based on feedback. Start on adding meta-analysis component to H2

---
title: "Codebook created on 2024-02-14 at 2024-02-14 09:47:30.71879"
output: github_document
---

@@

## Dataset description
The data contains 9 cases and 4 variables.

@@

```{r}
summaries <- read.csv("codebook_plot_23_data_reported_alpha.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2024-02-16 at 2024-02-16 14:19:42.46426"
output: github_document
---

@@

## Dataset description
The data contains 471 cases and 7 variables.

@@

```{r}
summaries <- read.csv("codebook_data_5.1.2_clean.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2024-02-16 Scripts/Manuscript/manuscript_v.master_thesis.Rmd
starting to restructure the article based on feedback. Start on adding meta-analysis component to H2

keywords          : "reliability, measurement, measurement reporting, replicability, construct validity"
wordcount         : "X"

@@

As a first step it is worth investigating what the state of measurement error is in original and psychological research, in order to assess the scope of @stanley2014expectations's findings in practice. Thus, this study investigated the following:

>>>>

keywords          : "reliability, measurement, measurement reporting, replicability, construct validity"
wordcount         : "194"

@@

As a first step it is worth investigating what the state of measurement error is in original and replication research in psychology, in order to assess the scope of @stanley2014expectations's findings in practice. Thus, this study investigated the following:
